Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-24 demystify.tex
Updates from Overleaf

\paragraph*{Not any harder than other countries} First, applying to a good US university \emph{should not} be any harder than at schools in other countries. It might even be more flexible since CS PhD in the US \emph{do not} require having an MS or a research topic, proposal, or adviser in advance (\autoref{sec:non-us-differences} compares CS PhD study in the US to other countries). It doesn't even require having a CS background (\autoref{sec:non-stem}).
If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan, and Australia, then you will surely have a chance in the US as well.

>>>>

\paragraph{Not any harder than other countries} First, applying to a good US university \emph{should not} be any harder than at schools in other countries. It might even be more flexible since CS PhD in the US \emph{do not} require having an MS or a research topic, proposal, or adviser in advance (\autoref{sec:non-us-differences} compares CS PhD study in the US to other countries). It doesn't even require having a CS background (\autoref{sec:non-stem}).
If you believe you have a chance in other countries, e.g., South Korea, Singapore, Germany, UK, Japan, and Australia, then you will surely have a chance in the US as well.
